---
title: "Lab 1"

author: "Emmanuel Robi"

date: "January 22, 2019"

output: html_document

---
```{r Packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

```{r DATA, include = FALSE}
(echo = TRUE)
###Collect data from the "China_EO_49to17.csv" file
Data <- read.csv("China_EO_49to17.csv", fileEncoding = "latin1")
```

#Part 1.1
  Based off the “All China Data Center” our assumption why some cities like Beijing and Shanghai are included in this list of provinces is due to population size. We noted many provinces with a population with 2,000,000 persons or more were considered “Super Large-sized cities”. 
  Looking in the database there is missing data on some provinces and cities which may be due to the fact that there just wasn’t data collected in the region or data collected was incorrectly. Much of the data comes from the year 2000. On an atlas the part of the People’s Republic of China that may people don’t really focus on is Western China. People are more focused on the eastern parts of China. 
  
#Part 1.2
  It would be more reliable to use older data than current data because of how unreliable China’s information is. There was a lot of faking of data in the 90’. The data between 2000-2011 is considered the most accurate give or take. According to Bloomberg, “If the official data lacks credibility, alternative narratives—like an economy on the verge of a hard landing—can take hold,” says Tom Orlik. To validate this, Economist writes “And China’s national GDP figure is laughably out of line with the sum of its provincial GDP figures. The various levels of government cannot keep their statistical stories straight.” The article articulates on how China has data that doesn’t correspond with other information discrediting the information. Since China has a difficult time concluding there true worth, it has gained a reputation to produce false information. Sara from Forbes writes, “But after years of producing growth even in the darkest of circumstances, China has gained a reputation for possibly overestimating its growth rate.” This further recognizes how the more time goes by, the more unreliable China’s data actually is. 

#Part1 Citations
https://www.bloomberg.com/news/articles/2018-04-19/china-s-economic-stats-have-a-credibility-problem

https://www.economist.com/finance-and-economics/2018/07/07/chinas-statistics-are-bad-many-criticisms-of-them-are-worse 

https://www.forbes.com/sites/sarahsu/2017/01/23/chinas-gdp-numbers-can-we-trust-the-data/ 

https://www.bloomberg.com/news/articles/2018-04-19/china-s-economic-stats-have-a- 


#Part 2.2
```{r PART2.2, include = TRUE}
###Create plot that is imported from the Year and Beijing_Enterprise columns
p <-ggplot(data = Data, aes(Year, Beijing_Enterprise))

###Imports third colum from the Tianjin_Enterprise column changing the bar to a different shade of blue 
p +geom_bar(stat="identity", aes(fill =Tianjin_Enterprise))
```

#Part 3.5 
```{r PART3.5A, include = TRUE}
###Create plot that is imported from year and Hebei_Enterprise columns 
Test1 <-ggplot(data = Data, aes(Year, Hebei_Enterprise))

###Imports third column from the Shaanxi_Enterprise column changing the bar to a different shade of blue
Test1 +geom_bar(stat="identity", aes(fill =Shaanxi_Enterprise))

#Columns Hebei_Enterprise and Shaanxi_Enterprise during the same years shows a correlation. The provinces show correlation in incline and decline during the same periods of time.
```

```{r PART3.5B, include = TRUE}
###Create plot that is imported from year and Shanghai_Enterprise columns 
Test2 <-ggplot(data = Data, aes(Year, Shanghai_Enterprise))

###Imports third column from the Liaoning_Enterprise column changing the bar to a different shade of blue
Test2 +geom_bar(stat="identity", aes(fill =Liaoning_Enterprise))

#Columns Shanghai_Enterprise and Liaoning_Enterprise during the same years show a correlation later in the years. Earlier, there doesnt seem to be any correlation
```

```{r PART3.5C, include = TRUE}
###Create plot that is imported from year and Zhejiang_Enterprise columns 
Test3 <-ggplot(data = Data, aes(Year, Zhejiang_Enterprise))

###Imports third column from the Ningxia_Enterprise column changing the bar to a different shade of blue
Test3 +geom_bar(stat="identity", aes(fill =Ningxia_Enterprise))

#Columns Zhejiang_Enterprise and Ningxia_Enterprise during the same years show a correlation. The provinces show correlation in incline and decline during the same period of time.
```
