---
title: "Lab 1 Part 3.3"
author: "Jamie Marken"
date: "January 24, 2019"
output: html_document
---


```{r library, include=FALSE}
library(tidyverse)
```

```{r data, echo=FALSE}
data <- read.csv("mychinadatafor_lab1formarkdown.csv")
```

```{r ratio, echo=FALSE}
barplot(height=data$Gansu_Output.Enterprise, names.arg = seq(1949,2017), ylab="Output per Enterprise", xlab="Year", main="Gansu Province")

#Made barplot for Gansu Province
```
  
  Within the Gansu Province, the monetary worth of enterprises in Gansu Province began to increase steadily in 1998 to 2000. This ratio then increased sharply up to 2017.





```{r beijing, echo=FALSE}
barplot(height=data$Beijing_Output.Enterprise, names.arg = seq(1949,2017), ylab="Output per Enterprise", xlab="Year", main = "Beijing")

#Made barplot for Beijing
```


For Beijing, the monetary worth of Beijing's enterprises increased from 1998 to 2007. From 2010 to 2012, we can see a sharp increase in this ratio up to 2017. 


``` {r recode Shanghai, echo=FALSE}


#tw <- is.na(data$Shanghai_Output)

#data$Shanghai_Output[tw] <- 0

data$Year <- data$ï..Year
data$Year <- substring(data$Year,5)
data$Year <- as.numeric(data$Year)

shang_data <- data %>%
  select(Year, Shanghai_Output, Shanghai_Enterprise) %>%
  mutate(Shanghai_Output.Enterprise = Shanghai_Output/Shanghai_Enterprise)

#Recoding Shanghai data to omit the symbols in the "Year" column
```

```{r shanghai, echo=FALSE}
barplot(height=shang_data$Shanghai_Output.Enterprise, names.arg = seq(1949,2017), ylab="Output per Enterprise", xlab="Year", main = "Shanghai")
        
#Made barplot for Shanghai        

```


From 1949 to 1991, the monetary worth of Shanghai's enterprises steadily grew. In 1995, this ratio grew sharply up to 2017.

